`SimSurvey`: an `R` package for simulation testing the design and analysis of fisheries-independent trawl surveys

### 2019-05-30 analysis/paper/sim_survey_paper.Rmd
Start to re-work the introduction

Fisheries-independent trawl surveys have become an increasingly important research tool for the management of dynamic fish stocks. These surveys provide reliable indices of population abundance as well as estimates of various population characteristics such as length and age frequencies [@Pennington1998]. While costly to obtain, this information forms the basis of of many stock assessments models used throughout the world. Effective and informed management decisions therefore require surveys that maximize information while minimizing the expense of data collection. Determining the number of samples required to adequately characterize a fish population is particularly challenging since data tend to be collected across one or more stages [@Aanes2015]. Optimal survey design is further complicated by the fact that trawls sample clusters of fish that tend to have similar characteristics, such as length, age and stomach contents. This phenomenon results in samples with positive intra-haul correlation, which can markedly reduce the effective sample size for estimating length and age frequencies of the target population [@Pennington1994; @Pennington2002; @Stewart2014]. The complexities of multi-stage sampling and intra-haul correlation make it difficult to answer the question *"how much sampling is enough?"*

@@

Again, this function retains all the objects listed in the output of `sim_distribution` and adds data.tables that detail the set locations (`setdet`) and sampling details (`samp`). Catchability corrected abundance matrices, named `I` and `I_at_length`, are also produced and added to the output; these matrices are useful for comparing the true abundance available to the survey to abundance estimates obtained using survey-based or model-based analyses of the simulated survey data. Specific surveys can be explored using the `plot_survey` function, which uses plotly [@sievert2018] and crosstalk [@cheng2016] in the background to link the bubble plot of aggregate set catch to the histogram of lengths and ages sampled to facilitate explorations of set-specific catches. The plots generated below have been combined here into a static plot for this paper (Figure \@ref(fig:survey)).

@@

The case study used here provides one example of ways in which **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are inextricably linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

- Feedback and advice: Aaron Adamack, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Keith Lewis, Derek Osborne, Pierre Pepin, Dwayne Pittman, Don Power, Craig Purchase, Greg Robertson, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote, Keith Lewis and Greg Robertson for a review of a previous version of this manuscript
- NSERC visiting-fellow program

>>>>

It is well known that the accuracy and reliability of any population monitoring program hinges on good survey design and analysis. Ideally, the design and analysis of any large and costly survey should be simulation tested before embarking on expensive field programs. This is especially true for the large-scale and costly fisheries-independent trawl surveys conducted by numurous regional fisheries management organizations. These surveys have become an increasingly important research tool for the management of dynamic fish stocks as they provide indices of population abundance as well as estimates of various population characteristics such as length and age frequencies [@Pennington1998]. While costly to obtain, this information forms the basis of of many stock assessments used throughout the world. Efficient, effective and informed management decisions therefore require surveys and analyses that maximize information while minimizing the expense of data collection. Solving this optimization problem is not a trivial task given the complexity of the population processes we aim to represent and the multi-stage nature of the typical sampling program.

The complexity of the system and the surveys may be why simulation tests of the full sampling and analylicical pathway are rare. Simulations provide a playground of sorts...multiple frameworks...few accessible...

Fisheries-independent trawl surveys have become an increasingly important research tool for the management of dynamic fish stocks. These surveys provide indices of population abundance as well as estimates of various population characteristics such as length and age frequencies [@Pennington1998]. While costly to obtain, this information forms the basis of of many stock assessments models used throughout the world. Effective and informed management decisions therefore require surveys that maximize information while minimizing the expense of data collection. Determining the number of samples required to adequately characterize a fish population is particularly challenging since data tend to be collected across one or more stages [@Aanes2015]. Optimal survey design is further complicated by the fact that trawls sample clusters of fish that tend to have similar characteristics, such as length and age. This phenomenon results in samples with positive intra-haul correlation, which can markedly reduce the effective sample size for estimating length and age frequencies of the target population [@Pennington1994; @Pennington2002; @Stewart2014]. The complexities of multi-stage sampling and intra-haul correlation make it difficult to answer the question *"how much sampling is enough?"* Moreover, the answer to this question is inextricably linked with the way in witch these data are analyzed.

While analyses of fisheries-independent survey data has typically been confined to design-based approaches [e.g. stratified-random survey data tend to be analyzed using standard stratified-analysis formulae;  @Cochran1977], there are a growing number of model-based approaches for analyzing such data [e.g. @smith1990; @Berg2014; @Thorson2015]. The merits of both approaches have long been debated, however, simulation tests of the full sampling and analylitical pathway are rarely conducted. This is especially true for design- or model-based estimates of abundance-at-age, which is a criticial input to any age-based stock assessment model. Ideally, the design and analysis of any large and costly survey should be simulation tested before embarking on an expensive field program.

@@

Again, this function retains all the objects listed in the output of `sim_distribution` and adds data.tables that detail the set locations (`setdet`) and sampling details (`samp`). Catchability corrected abundance matrices, named `I` and `I_at_length`, are also produced and added to the output; these matrices are useful for comparing the true abundance available to the survey to abundance estimates obtained using design-based or model-based analyses of the simulated survey data. Specific surveys can be explored using the `plot_survey` function, which uses plotly [@sievert2018] and crosstalk [@cheng2016] in the background to link the bubble plot of aggregate set catch to the histogram of lengths and ages sampled to facilitate explorations of set-specific catches. The plots generated below have been combined here into a static plot for this paper (Figure \@ref(fig:survey)).

@@

The case study used here provides one example of ways in which **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

- Feedback and advice: Aaron Adamack, Jonathan Babyn, Alejandro Buren, Noel Cadigan, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Keith Lewis, Derek Osborne, Pierre Pepin, Dwayne Pittman, Don Power, Craig Purchase, Greg Robertson, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Package contributions: Jonathan Babyn, Greg Robertson
- Dave Cote, Keith Lewis and Greg Robertson for a review of a previous version of this manuscript
- NSERC visiting-fellow program
